Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-26 paper/main.tex
typos

% ---------- AV control contrasts ----------
% 6 nothing 7 nothing 8 nothing 9 nothing
%10 se_new > se_old (nouns but in AV stimulus): LOC (l/r) right PPA, bilateral
%sup. lat. occ. c., sup. parietal lobe (right)

@@

% intro
For each naturalistic stimus, we created several control contrasts.
% movie contrasts: not cut condition vs. cuts
To test for XYZ\todo{yes, to test what?} within the movie fMRI data, we created
four contrasts that compared hemodynamic activity during frames within movie
shots (\texttt{no\_cut} category) with movie cut related categories
(Tab.~\ref{tab:contrasts}).
% results
None of these four contrasts yielded a significant cluster.
%
Null results of control contrasts comparing frames within movie shots to frames
immediately after a cut suggest that XYZ.
%
\todo[inline]{concluding statement}

% \texttt{se\_new} (nouns) is r$\approx$0.3 correlated with \texttt{vse\_new}
% (cuts); \texttt{se\_old} (nouns) is r$\approx$0.4 correlated with
% \texttt{vse\_old}.
The inspection of correlations of regressors across stimuli
(Fig.~\ref{fig:reg-corr}) showed a moderate correlation among cuts to a setting
depicted for the first time (\texttt{vse\_new}) and nouns indicating a switch to
a setting occurring for the first time (\texttt{se\_new}), and cuts to a
recurringly depicted setting ({\texttt{vse\_old}) and nouns indicating a switch
a recurring setting (\texttt{se\_old}.
%
Hence, we created a contrast that used the audio-description's nouns on the
movie data ({\texttt{se\_new} > \texttt{se\_old}).
% results
The contrasts yielded a significant cluster in the right PPA and bilateral
clusters in the superior lateral occipital cortices (the right hemispheric
cluster extending into the superior parietal cortex).
%
Results suggest that XYZ.
%
\todo[inline]{concluding statement? That last contrast was originally done to
check that "soundscape at moment of cuts thing" but this is obsolete now}

@@

% AD stimulus
Finally for the analysis of the audio-description, we created control contrasts
based on events of the annotated movie cuts (Tab.~\ref{tab:contrasts}) in
order to test XYZ.
% results
Two of five contrasts yielded significant clusters.
% contrast 9
Contrast 9 (\texttt{vse\_new > pe\_old}) revealed one significant cluster in the
left inferior prefrontal cortex (pars triangularis) and right ventral
precuneus/posterior cingulate gyrus.
% contrast 12
Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
one cluster in the right posterior hippocampus.  \todo{explanation?}
%
Overall results from the negative control contrast of the audio-description's
data suggest that XYZ.
%
\todo[inline]{concluding statement?}.

>>>>

% ---------- AV control contrasts ----------
% 6: nothing; 7 nothing; 8: nothing; 9: nothing; 10 se_new > se_old (nouns but
% in AV stimulus): LOC (l/r) right PPA, bilateral, sup. lat. occ. c., sup.
% parietal lobe (right)

@@

% intro
For each naturalistic stimulus, we created several control contrasts.
% movie contrasts: not cut condition vs. cuts
To test for XYZ\todo{yes, to test what?} within the movie fMRI data, we created
four contrasts that compared hemodynamic activity during frames within movie
shots (\texttt{no\_cut} category) with movie cut related categories
(Tab.~\ref{tab:contrasts}).
% results
None of these four contrasts yielded a significant cluster.
%
Null results of control contrasts comparing frames within movie shots to frames
immediately after a cut suggest that XYZ.
%
\todo[inline]{concluding statement}

% \texttt{se\_new} (nouns) is r$\approx$0.3 correlated with \texttt{vse\_new}
% (cuts); \texttt{se\_old} (nouns) is r$\approx$0.4 correlated with
% \texttt{vse\_old}.
The inspection of correlations of regressors across stimuli
(Fig.~\ref{fig:reg-corr}) showed a moderate correlation among cuts to a setting
depicted for the first time (\texttt{vse\_new}) and nouns indicating a switch to
a setting occurring for the first time (\texttt{se\_new}), and cuts to a
recurringly depicted setting ({\texttt{vse\_old}) and nouns indicating a switch
a recurring setting (\texttt{se\_old}.
%
Hence, we created a contrast that used the audio-description's nouns on the
movie data ({\texttt{se\_new} > \texttt{se\_old}).
% results
The contrasts yielded a significant cluster in the right [but not anterior] PPA
and bilateral clusters in the superior lateral occipital cortices (the right
hemispheric cluster extending into the superior parietal cortex).
%
Results suggest that XYZ.
%
\todo[inline]{concluding statement? That last contrast was originally done to
check that "soundscape at moment of cuts thing" but this is obsolete now}

@@

% AD stimulus
Finally for the analysis of the audio-description, we created control contrasts
based on events of the annotated movie cuts (Tab.~\ref{tab:contrasts}) in
order to test XYZ.
% results
Two of five contrasts yielded significant clusters.
% contrast 9
Contrast 9 (\texttt{vse\_new > pe\_old}) revealed one significant cluster in the
left inferior prefrontal cortex (pars triangularis) and right ventral
precuneus/posterior cingulate gyrus.
% contrast 12
Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
one cluster in the right posterior hippocampus.  \todo{not PPA! explanation?}
%
Overall results from the negative control contrast of the audio-description's
data suggest that XYZ.
%
\todo[inline]{concluding statement?}.
